Buildtime Trend : What's trending in your build process

### 2015-04-02 buildtimetrend/presentation.tex
add slides about future and welcoming contributors
add acknowledgments

@@

  \begin{frame}
    \frametitle{Lessons learned}
    \begin{itemize}
      \item start simple
      \item (re)use as much existing tools as possible
      \item start with what you know, learn new skills as you progress
      \item try, even if it is all scary at first
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Dieter Adriaenssens - \href{https://twitter.com/dcadriaenssens}{\small{@dcadriaenssens}}
    \vfill
    Buildtime Trend
    \begin{itemize}
      \item Website : \href{https://buildtimetrend.github.io/}{\small{https://buildtimetrend.github.io/}}
      \item Service : \href{https://buildtimetrend.herokuapp.com/}{\small{https://buildtimetrend.herokuapp.com/}}
      \item Twitter : \href{https://twitter.com/buildtime_trend}{\small{@buildtime\_trend}}
    \end{itemize}
  \end{frame}
\end{document}

>>>>

    \frametitle{Future development}
      \item caching for badges and dashboard charts
      \item service : seperate worker for build job processing
      \item support private Github repos
      \item support other CI platforms (Jenkins, ...)
      \item more and improved metrics and trends
    \frametitle{Contributions welcome}
      \item use and test the service
      \item report bugs
      \item suggest improvements
      \item clone the project and send pull requests
        \item implement a feature
        \item fix a bug
        \item add a new chart
        \item improve dashboard layout
        \item \ldots

@@

    \frametitle{Lessons learned}
      \item start simple
      \item (re)use as much existing tools as possible
      \item start with what you know, learn new skills as you progress
      \item try, even if it is all scary at first
    \frametitle{Acknowledgements}
    Big thanks to
      \item Josh (\href{https://twitter.com/dzello}{@dzello}) and the other nice people of Keen.io, for their invaluable support!
      \item \href{https://twitter.com/thomasbonte}{@thomasbonte} for introducing me to Lean Startup principles
      \item Alex for telling me about CherryPy
      \item all the \href{https://github.com/buildtimetrend/python-lib/wiki/Credits}{services} that power the project
      \item my friends and family
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    Dieter Adriaenssens - \href{https://twitter.com/dcadriaenssens}{\small{@dcadriaenssens}}
    Buildtime Trend
      \item Website : \href{https://buildtimetrend.github.io/}{\small{https://buildtimetrend.github.io/}}
      \item Twitter : \href{https://twitter.com/buildtime_trend}{\small{@buildtime\_trend}}
\end{document}
